---
title: "R Notebook"
output: html_notebook
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(waffle)
library(hrbrthemes)
library(extrafont)
```

The data was downloaded from [here](https://knoema.com/data/pets-population+birds)

## Data

```{r}
df <- read.csv("Pets_data.csv", header = TRUE, stringsAsFactors = TRUE)
head(df)
```

```{r}
str(df)
```

We have 29 countries and 4 different pets. In the case of Population variable we have the next descriptive statistics:

```{r}
summary(df)
```

The minimum value is 38000 and the maximum es 191001000 which means that the difference is in 5 grades of magnitude. To visualize this differences we have different options like divide all with millons or get the logaritmic. We would try dividing the values by millons

```{r}
df <- df %>% mutate(ByMillon = Population/1e+06)
head(df)
```

We want to prepare the data to make a waffle chart so to test we would select only one country, for example, Russian Federation, why not?

```{r}
df_russia <- df %>%  filter(Country == "Russian Federation")
df_russia
```

```{r}
df_russia %>% 
  count(Pets, wt = Population) %>% 
  ggplot(aes(fill = Pets, values = n)) +
  geom_waffle(n_rows = 10,colour = "white", flip = TRUE, size = 0.33, make_proportional = TRUE) +
  scale_fill_manual(
    name = NULL,
    values = c("#a40000", "#c68958", "#ae6056", "#aaaaaa"),
    labels = c("Birds", "Cats", "Dogs", "Fish")
  ) + 
  coord_equal() +
  theme_ipsum_rc(grid = "") +
  theme_enhance_waffle() +
  theme(legend.key.height = unit(2.25, "line")) +
  theme(legend.text = element_text(size = 10, hjust = 0, vjust = 0.75))
```

Now with two countries

```{r}
df_countries <- df %>%  filter(Country %in% c("Russian Federation", "China")) %>% 
  mutate(ByMillon = ceiling(ByMillon))
df_countries
```

```{r}
ggplot(df_countries, aes(fill = Pets, values = ByMillon)) +
  geom_waffle(color = "white", size = 0.25, n_rows = 10, flip = TRUE, make_proportional = FALSE) +
  facet_wrap(~Country, nrow = 1, strip.position = "bottom") +
  scale_x_discrete() +
  scale_y_continuous(labels = function(x) x * 10, # make this multiplyer the same as n_rows
                     expand = c(0,0)) +
  ggthemes::scale_fill_tableau(name = NULL) +
  coord_equal() + 
  theme_minimal(base_family = "Roboto Condensed") +
  theme(panel.grid = element_blank(), axis.ticks.y = element_line()) +
  guides(fill = guide_legend(reverse = TRUE))
```

```{r}
fa_grep("cat|dog|fish|bird|dove")
```


## Using pictograms


```{r}
df_russia %>% mutate(ByMillon = ceiling(ByMillon)) %>% 
  ggplot(aes(label = Pets, values = ByMillon, color = Pets)) +
  geom_pictogram(n_rows = 10, make_proportional = TRUE, family = "Font Awesome 5 Free Solid", size = 7) +
  scale_color_manual(
    name = NULL,
    values = c(      
      Birds = "green",
      Cats = "black",
      Dogs = "brown",
      Fish = "blue")
  ) +
  scale_label_pictogram(
    name = NULL,
    values = c(
      Birds = "dove",
      Cats = "cat",
      Dogs = "dog",
      Fish = "fish"
    )
  ) +
  coord_equal() +
  theme_ipsum_rc(grid = "") +
  theme_enhance_waffle() +
  theme(legend.key.height = unit(2.25, "line")) +
  theme(legend.text = element_text(size = 10, hjust = 0, vjust = 0.75))
```







